\documentclass[10pt,a4paper,sans]{moderncv}

\moderncvstyle{casual}

\moderncvcolor{blue}

\usepackage[scale=0.80]{geometry}
\setlength{\hintscolumnwidth}{3.00cm}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\name{Benjamín}{Pondal}

\begin{document}

\maketitle

\section{\textsc{Personal Information}}
\cvitem{Residence}{Martínez, Buenos Aires}
\cvitem{Mobile Phone}{+54 11 4038-7105}
\cvitem{Email}{benjaminpondal@hotmail.com}
\cvitem{GitHub Profile}{\url{https://github.com/DvorakXL}}

\section{\textsc{Education}}
\cventry{2009 - 2021}{Bachelor in Economics and Administration}{San Gabriel School}{}{}{
    \textbf{Overall Average} 8.50
}
\cventry{2022 - present}{Bachelor's Degree in Computer Science}{University of Buenos Aires}{Faculty of Exact and Natural Sciences}{}{
    \textbf{Expected graduation date} December 2028
}

\section{\textsc{Experience}}
\cventry{January 2025}{Full Stack Developer}{Renvance}{Startup}{}{
    \begin{itemize}
        \item \textbf{Backend:} REST API design with Python and AWS services management (Lambda, S3).
        \item \textbf{Frontend:} Interactive component creation in React.js with state integration via Redux.
        \item \textbf{Testing:} End-to-end testing using Cypress.
    \end{itemize}
    \textbf{Reference contact:} \href{mailto:alejandro.mildiner@renvance.com}{alejandro.mildiner@renvance.com}
}
\cventry{2023 - Present}{Ethical Hacking and Cybersecurity}{HackerOne}{}{}{
    Identification and reporting of vulnerabilities in web platforms:
    \begin{itemize}
        \item High severity Cross Site Scripting vulnerability in Reddit (social network used by more than 70 million daily active users).
              \newline \url{https://hackerone.com/reports/1962645}
        \item Medium severity Cross Site Scripting vulnerability in Mail.ru (Russian email service used by more than 30 million users).
              \newline \url{https://hackerone.com/reports/1121980}
    \end{itemize}
    \textbf{Technical approach:} Reconnaissance with Burp Suite, manual and automated exploitation using Kali Linux, PoC writing.
}

\section{\textsc{Projects}}
\cvlistitem{
    Development of Minecraft Mods (Java - Forge API). Use of object-oriented programming to extend base game classes and add new mechanics.
}
\cvlistitem{Development of a Discord Bot using NodeJS and consuming Steam API. Locally served and providing services to more than 10 private servers.}
\cvlistitem{Video game development in Unity and Godot implementing design patterns for Object-Oriented Programming such as Finite State Machines, Model View Controller and Factory Pattern.}

\section{\textsc{Technical Skills}}
\cvitem{Basic experience}{C\#, Java, TypeScript, Python, Unity, ReactJS, HTML, CSS, MySQL, AWS, Cypress, Unit Testing and Git.}

\section{\textsc{Languages}}
\cvdoubleitem{English}{Advanced level. Cambridge English: First (FCE)}{Spanish}{Native speaker.}

\end{document}
